---
output: html_document
editor_options: 
  chunk_output_type: console
---

Question
========
  
```{r setup, include=FALSE}
  # chunk defaults
  knitr::opts_chunk$set(echo = FALSE, eval=TRUE, results='hide', fig.show ='hide', comment=NA, message=FALSE)
  seed1 <- sample(1:9999,1)
```

## Setup instructions

- Execute the following lines
- Then answer all question below using the data set `cps`!

```{ }
library(AER)
set.seed(`r seed1`)
data('CPS1985')
cps <- CPS1985[sample(1:nrow(CPS1985), 150, TRUE),]
```


## Questions

```{r}
library(AER)
set.seed(seed1)
data('CPS1985')
cps <- CPS1985[sample(1:nrow(CPS1985), 150, TRUE),]
cl <- new_clozeL('Cloze Quiz Example')
```

**In MCQs, mark the answer choice that best completes the statement, answers the question or is closest to the precise answer.**  

# 1. Descriptive statistics

Males have more years of education than females on average in which of the following occupations? \#\#ANSWER1\#\#
```{r}
w <- tapply(cps$education, list(cps$gender, cps$occupation), FUN=mean)
opts <- colnames(w)
corrno <- which(w[1,]>w[2,])
cl <- add_mchoice(cl, options=opts, correctno=corrno, shuffle=FALSE, points=2, display='horizontal')
```

# 2. Regression

Estimate a regression model `m1` where logarithm of the hourly US$ `wage` dependents on `age` and `gender`.  
Use the results to answer the following questions.

a.  Test the hypothesis that both slope coefficients are equal to zero versus the alternative that at least one is not. Provide the corresponding $p$-value with *all* decimal places as inferred from the regression `summary`. \#\#ANSWER2\#\#
    ```{r}
    m1 <- lm(log(wage) ~ age + gender, data=cps)    
    fstat <- summary(m1)$fstatistic 
    pval <- pf(fstat[1],fstat[2],fstat[3],lower.tail=FALSE)
    cl <- add_num(cl, ans=c(pval,pval), tol=c(0.00001,0.01), points=2, pointfrac=c(100,10))
    ```
b.  The coefficient of `age` is \#\#ANSWER3\#\#
    ```{r}
    opts <- c('statistically significant at the 0.1% level.', 'statistically significant at the 1% level.', 'statistically significant at the 5% level.', 'statistically significant at the 10% level.', 'not statistically significant.')
    pans <- c(0.001, 0.01, 0.05, 0.1, 1)
    pval <- summary(m1)$coefficients['age','Pr(>|t|)']
    corrno <- which(pval <= pans)[1]
    cl <- add_schoice(cl, options=opts, correctno=corrno, shuffle=F, points=1)
    ```
c.  How much does the wage of females differ from that of males if they are of the same age? \#\#ANSWER4\#\#
    ```{r}
    cf <- coef(m1)
    cf_int <- cf['(Intercept)']
    cf_age <- cf['age']
    cf_gender <- cf['genderfemale']
    opts <- c(cf_gender, cf_age+cf_gender, cf_int+cf_age+cf_gender)
    opts <- paste0( rep( stdround(c(opts, opts*100, opts/100),3), each=2) , c(' $',' %'))
    corrno <- which(opts==paste0(stdround(cf_gender*100, 3), ' %'))
    cl <- add_schoice(cl, options=opts, correctno=corrno, shuffle=TRUE, points=1)
    ```
d.  If the variance of $u_i$ conditional on age and gender is constant, the regression error term is called \#\#ANSWER5\#\#
    ```{r}
    # if the answer in num or string questions is given as a vector, the are interpreted as alternative answer options which might give differing fractions of the maximum points possible
    ans <- c('homoskedastic','homoscedastic','homoskedasticity','homoscedasticity')
    cl <- add_string(cl, answer=ans, points=2, pointfrac=c(100,100,50,50))
    ```

```{r, results='asis'}
  print_answerlist(cl)
  print_metainfo(cl)
```
